A Comparison of Dimensionality Reduction Techniques for Robotic Motion Planning

### 2016-05-11 paper/paper.tex
RRT star done
added to paper

Dimensionality reduction is a key component of making robotic motion planning
fast and efficient. A rigid body has six degrees of freedom (DoF), so a
multi-link robot such as a humanoid or snake robot can have dozens or hundreds
of DoF. The rotational and translational transformations of a rigid body can be
described with the 3-dimensional Special Euclidean group (known as SE(3)).
SE(3) is homeomorphic to the topological space R3xRP3 (where RP3 is the
3-dimensional real projective plane). Therefore it is easy to imagine a
multi-link robot with an arbitrarily complex state space. The picture is
further complicated by the addition of obstacles into a robot's world. The
state space for motion planning, which must take into account both the robot
and obstacles, is called the configuration space.

@@

[RRT* algorithm]
[PRM* algorithm]

We used RRT* and PRM* in our project. The * indicates that these are the
asymptotically optimal versions of RRT and PRM (they are guaranteed to find the
optimal path as time goes to infinity). [Description of how RRT* and PRM* work]

The Probabilistic RoadMap algorithm has two phases: the preprocessing phase in which a roadmap is constructed by sampling random points in the C-space, and the query phase in which a graph search over the roadmap is made to connect initial and goal configurations.The map is constructed during the preprocessing phase by sampling random points in the C-space and then adding them to the nearest existing vertices in the roadmap. in

@@

\cite{wallar2015reactive}

\begin{algorithm}[ht] 
    \caption{PRM*}
    \label{algo:PRMstar}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $\Function{GetLocations}(\Var{r}, \Var{spl}, \Var{eventList}) \rightarrow$
        \STATE $\Var{locations} \leftarrow \Function{InitLocationList}()$
        \FORALL {$e \in \Var{eventList}$}
        \STATE $\Var{locations}.\Var{add}(\mathcal{L}_m(\Var{r}, \Var{spl}, \Var{eventList}, e.\Var{x}, e.\Var{y}))$
        \ENDFOR
        \STATE $\Var{centers} \leftarrow \Function{AffinityPropagation}(\Var{locations})$
        \COMMENT {\Var{centers} is a list of $(x, y, c)$ points where $c$ is the confidence}
        \RETURN $\Var{centers}$

>>>>

Dimensionality reduction is a key component of making robotic motion planning
fast and efficient. A rigid body has six degrees of freedom (DoF), so a
multi-link robot such as a humanoid or snake robot can have dozens or hundreds
of DoF. The rotational and translational transformations of a rigid body can be
described with the 3-dimensional Special Euclidean group (known as SE(3)).
SE(3) is homeomorphic to the topological space R3xRP3 (where RP3 is the
3-dimensional real projective plane). Therefore it is easy to imagine a
multi-link robot with an arbitrarily complex state space. The picture is
further complicated by the addition of obstacles into a robot's world. The
state space for motion planning, which must take into account both the robot
and obstacles, is called the configuration space \cite{lavalle2006planning}.

@@

We used RRT* and PRM* in our project. The * indicates that these are the
asymptotically optimal versions of RRT and PRM (they are guaranteed to find the
optimal path as time goes to infinity).

The Probabilistic RoadMap algorithm has two phases: the preprocessing phase in which a roadmap is constructed by sampling random points in the C-space, and the query phase in which a graph search over the roadmap is made to connect initial and goal configurations.The map is constructed during the preprocessing phase by sampling random points in the C-space and then adding them to the vertices in the roadmap within a certain radius of the point. PRM can be elevated to the asymptotically optimal PRM* by defining the radius to be a function of the number of vertices and the dimensionality of the space.

The Rapidly-expanding Random Tree algorithm works by building up a tree from the initial configuration to the goal configuration. Starting at the initial configuration as the root, it incrementally attempts to add randomly selected samples to the tree until it reaches the goal configuration. RRT* differs from RRT in that whenever a new node is added to the tree, connections are also tested to the new node from every other node that is within a certain radius from the new node. The the tree is pruned so that edges that are not part of the shortest path from the root of the tree to the new node are removed.

@@

\begin{algorithm}[ht] 
    \caption{$\Function{PRM}^*$~\cite{karaman2011sampling}}
    \label{algo:MS}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $V \leftarrow \{x_{init}\} \cup \{\Var{SampleFree}_i\}_{i=1,\ldots,n}$
        \STATE $E \leftarrow \emptyset$
        \FORALL{$v \in V$}
            \STATE $U \leftarrow \Function{Near}(G = (V, E), v,
            \gamma \cdot \Function{PRM}(\log(n) / n) ^ {1 / d})
            \backslash \{v\}$
            \FORALL{$u \in U$}
                \IF{$\Function{CollisionFree}(v, u)$}
                    \STATE $E \leftarrow E \cup \{(v, u), (u, v)\}$
                \ENDIF
            \ENDFOR
        \ENDFOR
        \RETURN $G = (V, E)$
